Setting up Data

### 2020-04-21 src/SetupData.Rmd
switched adj_nMLH1 to MLH1

AP_mouse_table.MLH1_HQ <- ddply(MLH1_data[MLH1_data$quality < 5,], c("mouse"), summarise,
                        Nmice = length(unique(mouse)),
                        Ncells  = length(adj_nMLH1.foci),
                        mean_co = as.numeric(format(round(  mean(adj_nMLH1.foci, na.rm=TRUE), 3 ), nsmall=3) ),
                        cV = cv(adj_nMLH1.foci, na.rm=TRUE),
                        var = as.numeric(format(round(   var(adj_nMLH1.foci, na.rm=TRUE),3), nsmall=3)),
                        sd   = round(sd(adj_nMLH1.foci), 3),
                        se   = round(sd / sqrt(Ncells), 3),

@@

save.image("~./MLH1repo/data/MLH1/MLH1_data_setup_2.24.20.RData")

>>>>

AP_mouse_table.MLH1_HQ <- ddply(MLH1_data[MLH1_data$quality < 5,], c("mouse"), summarise,
                        Nmice = length(unique(mouse)),
                        Ncells  = length(nMLH1.foci),
                        mean_co = as.numeric(format(round(  mean(nMLH1.foci, na.rm=TRUE), 3 ), nsmall=3) ),
                        cV = cv(adj_nMLH1.foci, na.rm=TRUE),

                        var = as.numeric(format(round(   var(nMLH1.foci, na.rm=TRUE),3), nsmall=3)),
                        sd   = round(sd(nMLH1.foci), 3),
                        se   = round(sd / sqrt(Ncells), 3),

@@

save.image("~./MLH1repo/data/MLH1/MLH1_data_setup_4.21.20.RData")
